Supplemental data to ``ARTICLE TITLE''

### 2022-09-19 additional_files/additional_file_1.tex
Integrate the generation of signals with the Makefile; add genes for loci that have been cloned after Bandillo et al. (2017)
Add functionality for plotting the haplotypes and variants deduced from the k-mer analysis; work in progress
Test for existence of an alignment before trying to gather sequences at a locus; add k-mer plot for pubescence form, locus Pa1
Add manhattan plots for k-mers located on scaffolds; remove some figures from supplementary material; adjust some parameters in defining signal width and top p-value regions; adjust the signal coordinates for corrected dry weight; make som

\newcommand{\signalplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_signal}
	\caption{#1\_signal}
	\label{#1_signal}
\end{cfigure}

@@

\newcommand{\geneplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_gene}
	\caption{#1\_gene}
	\label{#1_gene}
\end{cfigure}

@@

@@

\manhattanplot{flower_color}
\signalplot{flower_color_W1}
\geneplot{flower_color_W1}
%\signalplot{flower_color_L1}
%\geneplot{flower_color_L1}

\manhattanplot{pubescence_color_all}
%\signalplot{pubescence_color_all_Td}
\signalplot{pubescence_color_all_T}
\geneplot{pubescence_color_all_T}

\manhattanplot{pubescence_color_nogray}
\signalplot{pubescence_color_nogray_Td}
%\signalplot{pubescence_color_nogray_T}
%\geneplot{pubescence_color_nogray_T}

\manhattanplot{seed_coat_color_all}
\signalplot{seed_coat_color_all_G}
\signalplot{seed_coat_color_all_T}
\geneplot{seed_coat_color_all_T}
\signalplot{seed_coat_color_all_O}
\signalplot{seed_coat_color_all_I}
\geneplot{seed_coat_color_all_I}
%\signalplot{seed_coat_color_all_R}
%\geneplot{seed_coat_color_all_R}

\manhattanplot{seed_coat_color_greenyellow}
\signalplot{seed_coat_color_greenyellow_G}
%\signalplot{seed_coat_color_greenyellow_T}
%\geneplot{seed_coat_color_greenyellow_T}
%\signalplot{seed_coat_color_greenyellow_O}
%\signalplot{seed_coat_color_greenyellow_I}
%\geneplot{seed_coat_color_greenyellow_I}
%\signalplot{seed_coat_color_greenyellow_R}
%\geneplot{seed_coat_color_greenyellow_R}

\manhattanplot{stem_termination_all}
%\signalplot{stem_termination_all_Dt2}
%\geneplot{stem_termination_all_Dt2}
\signalplot{stem_termination_all_Dt1}
\geneplot{stem_termination_all_Dt1}
%\signalplot{stem_termination_all_E3}
%\geneplot{stem_termination_all_E3}

\manhattanplot{stem_termination_sn}
%\signalplot{stem_termination_sn_Dt2}
%\geneplot{stem_termination_sn_Dt2}
\signalplot{stem_termination_sn_Dt1}
\geneplot{stem_termination_sn_Dt1}
%\signalplot{stem_termination_sn_E3}
%\geneplot{stem_termination_sn_E3}

\manhattanplot{hilum_color_all}
\signalplot{hilum_color_all_T}
\geneplot{hilum_color_all_T}
%\signalplot{hilum_color_all_O}
\signalplot{hilum_color_all_I}
\geneplot{hilum_color_all_I}
\signalplot{hilum_color_all_R}
\geneplot{hilum_color_all_R}
%\signalplot{hilum_color_all_W1}
%\geneplot{hilum_color_all_W1}

\manhattanplot{hilum_color_blackbrown}
%\signalplot{hilum_color_blackbrown_T}
%\geneplot{hilum_color_blackbrown_T}
%\signalplot{hilum_color_blackbrown_O}
%\signalplot{hilum_color_blackbrown_I}
%\geneplot{hilum_color_blackbrown_I}
\signalplot{hilum_color_blackbrown_R}
\geneplot{hilum_color_blackbrown_R}
%\signalplot{hilum_color_blackbrown_W1}
%\geneplot{hilum_color_blackbrown_W1}

\manhattanplot{hilum_color_rbr}
%\signalplot{hilum_color_rbr_T}
%\geneplot{hilum_color_rbr_T}
%\signalplot{hilum_color_rbr_O}
%\signalplot{hilum_color_rbr_I}
%\geneplot{hilum_color_rbr_I}
%\signalplot{hilum_color_rbr_R}
%\geneplot{hilum_color_rbr_R}
%\signalplot{hilum_color_rbr_W1}
%\geneplot{hilum_color_rbr_W1}

\manhattanplot{pod_color_all}
\signalplot{pod_color_all_L2}
\signalplot{pod_color_all_L1}
\geneplot{pod_color_all_L1}

\manhattanplot{pod_color_blbr}
%\signalplot{pod_color_blbr_L2}
\signalplot{pod_color_blbr_L1}
\geneplot{pod_color_blbr_L1}

\manhattanplot{pubescence_form_all}
\signalplot{pubescence_form_all_Pa1}
\signalplot{pubescence_form_all_Pa2}

\manhattanplot{pubescence_form_noerect}
\signalplot{pubescence_form_noerect_Pa1}
%\signalplot{pubescence_form_noerect_Pa2}

\manhattanplot{pubescence_density}
%\signalplot{pubescence_density_Pd1}
\signalplot{pubescence_density_Ps}
%\signalplot{pubescence_density_P1}
%\geneplot{pubescence_density_P1}

\manhattanplot{seed_coat_luster_all}
%\signalplot{seed_coat_luster_all_I}
%\geneplot{seed_coat_luster_all_I}
%\signalplot{seed_coat_luster_all_Bq}
%\signalplot{seed_coat_luster_all_B1}
\signalplot{seed_coat_luster_all_Hps}
\geneplot{seed_coat_luster_all_Hps}
\signalplot{seed_coat_luster_all_B}

\manhattanplot{seed_coat_luster_nointermediate}
%\signalplot{seed_coat_luster_nointermediate_I}
%\geneplot{seed_coat_luster_nointermediate_I}
%\signalplot{seed_coat_luster_nointermediate_Bq}
%\signalplot{seed_coat_luster_nointermediate_B1}
\signalplot{seed_coat_luster_nointermediate_Hps}
\geneplot{seed_coat_luster_nointermediate_Hps}
\signalplot{seed_coat_luster_nointermediate_B}

\manhattanplot{seed_coat_luster_dullshiny}
%\signalplot{seed_coat_luster_dullshiny_I}
%\geneplot{seed_coat_luster_dullshiny_I}
%\signalplot{seed_coat_luster_dullshiny_Bq}
%\signalplot{seed_coat_luster_dullshiny_B1}
\signalplot{seed_coat_luster_dullshiny_Hps}
\geneplot{seed_coat_luster_dullshiny_Hps}
\signalplot{seed_coat_luster_dullshiny_B}

\manhattanplot{corrected_dry_weight}
\signalplot{corrected_dry_weight_cdwGm17}

\manhattanplot{maturity_group}
%\signalplot{maturity_group_E1}
%\geneplot{maturity_group_E1}
%\signalplot{maturity_group_E2}
%\geneplot{maturity_group_E2}
%\signalplot{maturity_group_E3}
%\geneplot{maturity_group_E3}
%\signalplot{maturity_group_E4}
%\geneplot{maturity_group_E4}

\manhattanplot{oil}
\signalplot{oil_oilGm15}
%\signalplot{oil_oilGm20}

\manhattanplot{protein}
%\signalplot{protein_proteinGm15}
%\signalplot{protein_proteinGm20}

>>>>

% Defining a new command for signal plot figures
\newcommand{\signalplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_signal}
	\caption{#1\_signal}
	\label{#1_signal}
\end{cfigure}

@@

% Defining a new command for gene plot figures
\newcommand{\geneplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_gene}
	\caption{#1\_gene}
	\label{#1_gene}
\end{cfigure}

% Defining a new command for k-mer plot figures
\newcommand{\kmerplot}[1]{
	\begin{cfigure}
		\includegraphics[width = 6.5in]{#1_kmers}
		\caption{#1\_kmers}
		\label{#1_kmers}
	\end{cfigure}

@@

\begin{landscape} \footnotesize
	\begin{ThreePartTable}

		\begin{TableNotes}
		\item[a] test
		\end{TableNotes}

		\begin{longtable}{llcclccccl}

			\caption{Signals}\\
			\label{signals_table}\\

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & vg & Paragraph & k-mers  & Study \\
			\midrule \endfirsthead

			\caption[]{Signals \emph{(continued)}}\\

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & vg & Paragraph & k-mers  & Study \\
			\midrule
			\endhead

			\bottomrule
			Continued on next page \\
			\endfoot

			\bottomrule \insertTableNotes
			\endlastfoot
			\csvreader[head to column names,
			late after line=\\,
			late after last line=,
			before reading={\catcode`\#=12},
			after reading={\catcode`\#=6},
			/csv/separator=semicolon]%
			{../tables/signals_table.csv}{}{\Trait & \Locus & \Chromosome & \Pvalues & \Gene & \Platypus & \Vg & \Paragraph & \Kmers & \Study}

		\end{longtable}

	\end{ThreePartTable}

\end{landscape}
\clearpage

@@

\manhattanplot{flower_color}
%\manhattanplot{flower_color_scaffolds}
\signalplot{flower_color_W1}
\geneplot{flower_color_W1}
\kmerplot{flower_color_W1}
%\signalplot{flower_color_L1}
%\geneplot{flower_color_L1}

\manhattanplot{pubescence_color_all}
\manhattanplot{pubescence_color_all_scaffolds}
%\signalplot{pubescence_color_all_Td}
\signalplot{pubescence_color_all_T}
\geneplot{pubescence_color_all_T}
\kmerplot{pubescence_color_all_T}
\signalplot{pubescence_color_all_pcGm16}

\manhattanplot{pubescence_color_nogray}
%\manhattanplot{pubescence_color_nogray_scaffolds}
\signalplot{pubescence_color_nogray_Td}
\geneplot{pubescence_color_nogray_Td}
\kmerplot{pubescence_color_nogray_Td}
%\signalplot{pubescence_color_nogray_T}
%\geneplot{pubescence_color_nogray_T}

\manhattanplot{seed_coat_color_all}
%\manhattanplot{seed_coat_color_all_scaffolds}
%\signalplot{seed_coat_color_all_G}
%\geneplot{seed_coat_color_all_G}
%\signalplot{seed_coat_color_all_T}
%\geneplot{seed_coat_color_all_T}
%\signalplot{seed_coat_color_all_O}
\signalplot{seed_coat_color_all_I}
\geneplot{seed_coat_color_all_I}
%\signalplot{seed_coat_color_all_R}
%\geneplot{seed_coat_color_all_R}

\manhattanplot{seed_coat_color_greenyellow}
%\manhattanplot{seed_coat_color_greenyellow_scaffolds}
\signalplot{seed_coat_color_greenyellow_G}
\geneplot{seed_coat_color_greenyellow_G}
\kmerplot{seed_coat_color_greenyellow_G}
%\signalplot{seed_coat_color_greenyellow_T}
%\geneplot{seed_coat_color_greenyellow_T}
%\signalplot{seed_coat_color_greenyellow_O}
%\signalplot{seed_coat_color_greenyellow_I}
%\geneplot{seed_coat_color_greenyellow_I}
%\signalplot{seed_coat_color_greenyellow_R}
%\geneplot{seed_coat_color_greenyellow_R}

\manhattanplot{stem_termination_all}
%\manhattanplot{stem_termination_all_scaffolds}
%\signalplot{stem_termination_all_Dt2}
%\geneplot{stem_termination_all_Dt2}
\signalplot{stem_termination_all_Dt1}
\geneplot{stem_termination_all_Dt1}
\kmerplot{stem_termination_all_Dt1}
%\signalplot{stem_termination_all_E3}
%\geneplot{stem_termination_all_E3}

\manhattanplot{stem_termination_sn}
\signalplot{stem_termination_sn_stGm11}
%\manhattanplot{stem_termination_sn_scaffolds}
%\signalplot{stem_termination_sn_Dt2}
%\geneplot{stem_termination_sn_Dt2}
%\signalplot{stem_termination_sn_Dt1}
%\geneplot{stem_termination_sn_Dt1}
%\signalplot{stem_termination_sn_E3}
%\geneplot{stem_termination_sn_E3}

\manhattanplot{hilum_color_all}
\manhattanplot{hilum_color_all_scaffolds}
\signalplot{hilum_color_all_T}
\geneplot{hilum_color_all_T}
\kmerplot{hilum_color_all_T}
%\signalplot{hilum_color_all_O}
\signalplot{hilum_color_all_I}
\geneplot{hilum_color_all_I}
\kmerplot{hilum_color_all_I}
%\signalplot{hilum_color_all_R}
%\geneplot{hilum_color_all_R}
%\signalplot{hilum_color_all_W1}
%\geneplot{hilum_color_all_W1}

\manhattanplot{hilum_color_blackbrown}
%\manhattanplot{hilum_color_blackbrown_scaffolds}
%\signalplot{hilum_color_blackbrown_T}
%\geneplot{hilum_color_blackbrown_T}
%\signalplot{hilum_color_blackbrown_O}
%\signalplot{hilum_color_blackbrown_I}
%\geneplot{hilum_color_blackbrown_I}
\signalplot{hilum_color_blackbrown_R}
\geneplot{hilum_color_blackbrown_R}
%\signalplot{hilum_color_blackbrown_W1}
%\geneplot{hilum_color_blackbrown_W1}

\manhattanplot{hilum_color_rbr}
%\manhattanplot{hilum_color_rbr_scaffolds}
%\signalplot{hilum_color_rbr_T}
%\geneplot{hilum_color_rbr_T}
%\signalplot{hilum_color_rbr_O}
%\signalplot{hilum_color_rbr_I}
%\geneplot{hilum_color_rbr_I}
%\signalplot{hilum_color_rbr_R}
%\geneplot{hilum_color_rbr_R}
%\signalplot{hilum_color_rbr_W1}
%\geneplot{hilum_color_rbr_W1}

\manhattanplot{pod_color_all}
%\manhattanplot{pod_color_all_scaffolds}
\signalplot{pod_color_all_L1}
\geneplot{pod_color_all_L1}
\signalplot{pod_color_all_L2}

\manhattanplot{pod_color_blbr}
\signalplot{pod_color_blbr_pdcGm15}
%\manhattanplot{pod_color_blbr_scaffolds}
%\signalplot{pod_color_blbr_L2}
%\signalplot{pod_color_blbr_L1}
%\geneplot{pod_color_blbr_L1}

\manhattanplot{pubescence_form_all}
%\manhattanplot{pubescence_form_all_scaffolds}
\signalplot{pubescence_form_all_Pa1}
\geneplot{pubescence_form_all_Pa1}
\kmerplot{pubescence_form_all_Pa1}
\signalplot{pubescence_form_all_Pa2}
\signalplot{pubescence_form_all_pfGm04}
\signalplot{pubescence_form_all_pfGm15}

\manhattanplot{pubescence_form_noerect}
%\manhattanplot{pubescence_form_noerect_scaffolds}
\signalplot{pubescence_form_noerect_Pa1}
\geneplot{pubescence_form_noerect_Pa1}
%\signalplot{pubescence_form_noerect_Pa2}

\manhattanplot{pubescence_density}
%\manhattanplot{pubescence_density_scaffolds}
%\signalplot{pubescence_density_Pd1}
\signalplot{pubescence_density_Ps}
\geneplot{pubescence_density_Ps}
%\signalplot{pubescence_density_P1}
%\geneplot{pubescence_density_P1}

\manhattanplot{seed_coat_luster_all}
%\manhattanplot{seed_coat_luster_all_scaffolds}
%\signalplot{seed_coat_luster_all_I}
%\geneplot{seed_coat_luster_all_I}
%\signalplot{seed_coat_luster_all_Bq}
%\signalplot{seed_coat_luster_all_B1}
%\signalplot{seed_coat_luster_all_Hps}
%\geneplot{seed_coat_luster_all_Hps}
\signalplot{seed_coat_luster_all_B}
\geneplot{seed_coat_luster_all_B}
\signalplot{seed_coat_luster_all_sclGm09}

\manhattanplot{seed_coat_luster_nointermediate}
%\manhattanplot{seed_coat_luster_nointermediate_scaffolds}
%\signalplot{seed_coat_luster_nointermediate_I}
%\geneplot{seed_coat_luster_nointermediate_I}
%\signalplot{seed_coat_luster_nointermediate_Bq}
%\signalplot{seed_coat_luster_nointermediate_B1}
%\signalplot{seed_coat_luster_nointermediate_Hps}
%\geneplot{seed_coat_luster_nointermediate_Hps}
%\signalplot{seed_coat_luster_nointermediate_B}
%\geneplot{seed_coat_luster_nointermediate_B}

\manhattanplot{seed_coat_luster_dullshiny}
%\manhattanplot{seed_coat_luster_dullshiny_scaffolds}
%\signalplot{seed_coat_luster_dullshiny_I}
%\geneplot{seed_coat_luster_dullshiny_I}
%\signalplot{seed_coat_luster_dullshiny_Bq}
%\signalplot{seed_coat_luster_dullshiny_B1}
%\signalplot{seed_coat_luster_dullshiny_Hps}
%\geneplot{seed_coat_luster_dullshiny_Hps}
%\signalplot{seed_coat_luster_dullshiny_B}
\geneplot{seed_coat_luster_dullshiny_B}
\signalplot{seed_coat_luster_dullshiny_sclGm20}

\manhattanplot{corrected_dry_weight}
\manhattanplot{corrected_dry_weight_scaffolds}
\signalplot{corrected_dry_weight_cdwGm15}
\geneplot{corrected_dry_weight_cdwGm15}

\manhattanplot{maturity_group}
%\manhattanplot{maturity_group_scaffolds}
%\signalplot{maturity_group_E1}
%\geneplot{maturity_group_E1}
%\signalplot{maturity_group_E2}
%\geneplot{maturity_group_E2}
%\signalplot{maturity_group_E3}
%\geneplot{maturity_group_E3}
%\signalplot{maturity_group_E4}
%\geneplot{maturity_group_E4}

\manhattanplot{oil}
%\manhattanplot{oil_scaffolds}
\signalplot{oil_oilGm15}
\geneplot{oil_oilGm15}
%\signalplot{oil_oilGm20}

\manhattanplot{protein}
%\manhattanplot{protein_scaffolds}
%\signalplot{protein_proteinGm15}
%\signalplot{protein_proteinGm20}
